%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Independent Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
    \cventry
    {An IBM Watson powered intelligent lyrics sentiment analyzer.} % Info
    {Lyrics Analyzer - In Progress} % Project Name
    {PHP / JS} % LLang
    {Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {Key Features: Watson Powered, sentiment analysis, Materialize design, and iTunes top musics analysis.}
          %\item {Retrieve and process JSON from USGS in real time, and map earthquake locations on a 3D globe using WebGL.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {A WebGL-based earthquake real time visualization on a 3D globe.} % Info
    {Earthquake Real Time Visualization - Open Source} % Project Name
    {PHP / JS} % LLang
    {Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {Key Features: Real time earthquake update and mapping, JSON process, and API-based access.}
          %\item {Retrieve and process JSON from USGS in real time, and map earthquake locations on a 3D globe using WebGL.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {A web-based full featured Markdown notebook with client-side encryption.} % Info
    {Encrypted Notebook} % Project Name
    {PHP / Laravel} % LLang
    {Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {Key Features: Client-side AES-256 encryption, full featured Markdown editor,  zero knowledge of the content, and password-based sharing.}
      \end{cvitems}
    }

%---------------------------------------------------------
     \cventry 
    {A license activation dll with built-in anti-tamper features for both subscription-based and usage-based payment model.} % Info
    {License Activation System - Closed Source} % Project Name
    {C\#} % LLang
    {Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Anti-tamper features: Asymmetrical key, unique hardware fingerprint, timestamp \& counter verification, file hashing, log reporting.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {A Restaurant POS using MVC Architecture -  Model Only} % Info
    {Restaurant Point of Sale System - Open Source} % Project Name
    {JAVA} % LLang
    {Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {Key Features: Serialization, multi-threaded, ordering, receipt processing, daily reports, entree, inventory, and employee management.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
